Sleep Quality Estimation using Thigh-Mounted Accelerometer Data in Free Living Conditions

### 2023-02-17 presentation/index.qmd
assumptions for BA not met, see QQ-plots. Perform repeated measures, nonparametric BA.

---
title: "Sleep Quality Estimation using Machine Learning and Thigh-Mounted Accelerometer Data in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

@@

* I did free-living PSG recordings of sleep but...
  - Super fragile -> shitty data
  - Combersome and time consuming
  - free-living?
  - would surface skin temperature + acc be enough? Most likely needs HR

@@

data preparation, big time-consumer is handling raw acc data

only thigh data used. HSBC and other is only thigh data...

could be interesting to build models on thigh and hip ocmbined.

all zm recording is considered as in-bed (sensor problem?)

no sleep stages, only sleep/awake

sensor problems during sleep, up to 20 consecutive epochs (200 sec) are treated as sleep

## Exclusion Criteria {transition="fade"}

@@

::: {.fragment}
But as demonstrated by @walch_sleep_2019, a simple cosine function does the tricks just as well :)
:::

@@

## ROC Curves {.smaller transition="fade" .column-left}

@@

## {.smaller transition="fade" .column-left}

```{r}
source(here::here("presentation/code/tables_performance.R"))

tab_1
```

Performance of the models to predict each class <span style="color:gold">**seperately**</span>, i.e., "sleep" and "in-bed".

## {.smaller transition="fade" .column}

```{r}
tab_2
```

Performance of the models to predict each <span style="color:gold">**combined**</span> class, i.e., "sleep" + "in-bed".

## Bland-Altman Plots {.smaller transition="convex" .slide}

@@

```{r}
#| echo: false
source(here::here("presentation/code/ba_plots.R"))
plots$decision_tree[[1]]

@@

## In-bed classification flow {.smaller transition="zoom" .column}

@@

## Sleep classification flow {.smaller transition="zoom" .column}

@@

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds

>>>>

---
title: "Sleep Quality Estimation using Thigh-Mounted Accelerometer Data in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

@@

* I did free-living PSG recordings of sleep but...
  - Super fragile -> shitty data
  - Combersome and time consuming
  - free-living when wired up like a robot?
  - would surface skin temperature + acc be enough? Most likely needs HR

@@

- data preparation, big time-consumer is handling raw acc data
- only thigh data used. HSBC and other is only thigh data...
- all zm recording is considered as in-bed (sensor problem?)
- no sleep stages, only sleep/awake
- sensor problems during sleep, up to 20 consecutive epochs (200 sec) are treated as sleep

## Exclusion Criteria {transition="fade" .H2}

@@

::: {.fragment}
But as demonstrated by @walch_sleep_2019, a simple cosine function does the trick just as well :)
:::

@@

## ROC Curves {.smaller transition="fade"}

@@

## Lots of Metrics {.smaller transition="zoom" .H2}

::: {.column}
```{r}
source(here::here("presentation/code/tables_performance.R"))

tab1
```
:::

::: {.column}
```{r}
tab2
```
:::

## Bland-Altman Plots {.smaller transition="fade"}

@@

```{r}
#| echo: false
source(here::here("presentation/code/plot_ba.R"))
plots$decision_tree[[1]]

@@

## Bland-Altman Analysis {.smaller transition="fade" .H2}

```{r}
source(here::here("presentation/code/table_ba.R"))

tab_ba
```

## In-bed classification flow {.smaller transition="zoom" .H2}

@@

## Sleep classification flow {.smaller transition="zoom" .H2}

@@

- heteroscedasticity
- Cheung 2018 table 4: actigraphy provides a sufficiently narrow range of possible mean differences (CI 95%) clinical significant thresholds
- could be interesting to build models on thigh and hip ocmbined.
